### 2015-02-18 fundamentals/examples.tex
spell check and trailing whitespaces

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        Commelini-Sicart (COSI) fuel cycle simulator developed by the French
        Commissariat \`{a} l'\'{e}nergie atomique (CEA).

@@

    \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
        provides enriched UOX fuel as requested.  This facility has infinite
        production capacity.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled MOX
fuel with a higher preference then new UOX fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent UOX into a spent fuel market,
but spent MOX is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh UOX fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

>>>>

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

    \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
        provides enriched \gls{UOX} fuel as requested.  This facility has infinite
        production capacity.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled MOX
fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX into a spent fuel market,
but spent MOX is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

### 2015-02-18 fundamentals/fcsreqs.tex
spell check and trailing whitespaces

The proprietary concerns of research institutions and security constraints of
data within fuel cycle codes often restrict code access. A code's use is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
platform on which it relies is oftenrestricted or commercial.  However, \Cyclus
provide fully free and open access to all users
and developers, foreign and domestic.

@@

In addition to being inaccessible, the vast majority of fuel cycle simulators
are, effectively, inextensible. Typical fuel cycle simulator evelopment teams are insular, in
part due to accessiblity issues. Also, however, their frameworks contain
heuristics and assumptions that constrain developer additions.

>>>>

The proprietary concerns of research institutions and security constraints of
data within fuel cycle codes often restrict code access. A code's use is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
platform on which it relies is often restricted or commercial.  However, \Cyclus
provide fully free and open access to all users
and developers, foreign and domestic.

@@

In addition to being inaccessible, the vast majority of fuel cycle simulators
are, effectively, inextensible. Typical fuel cycle simulator development teams are insular, in
part due to accessibility issues. Also, however, their frameworks contain
heuristics and assumptions that constrain developer additions.

### 2015-02-18 fundamentals/impl.tex
spell check and trailing whitespaces

Lastly, \gls{UQ} is a process that is used on specific simulation
instantiations to statistically determine quality. \gls{UQ} is a process that applies 
to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
simulator, cannot make reliable statements about the uncertainty of a particular fuel 
cycle. Any \gls{UQ} results are applicable only to the scenario that is under 
analysis by the user. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development 
and in the domain of the expert user.

@@

\emph{\acrfull{CI}} is the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under \gls{CI}, every pull request (proposed code change) is tested independently immediately after 
it is proposed. Such tests are run on all officially supported platforms. 
\Cyclus uses a \gls{CI} platform called Polyphemus \cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
and temporary \Cyclus servers on the backend. These servers are hosted by 
the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of 
Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs 
the following actions:

>>>>

Lastly, \gls{UQ} is a process that is used on specific simulation
instantiations to statistically determine quality. \gls{UQ} is a process that applies
to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
simulator, cannot make reliable statements about the uncertainty of a particular fuel
cycle. Any \gls{UQ} results are applicable only to the scenario that is under
analysis by the user. \Cyclus is not a panacea for due diligence on behalf of the fuel
cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
and in the domain of the expert user.

@@

\emph{\acrfull{CI}} is the idea that software should be tested and validated
as it is being developed, rather than as a final stage in a longer development
cycle.  Under \gls{CI}, every pull request (proposed code change) is tested independently immediately after
it is proposed. Such tests are run on all officially supported platforms.
\Cyclus uses a \gls{CI} platform called Polyphemus
\cite{scopatz_polyphemus_2014}. Polyphemus serves as an intermediary between GitHub pull requests on the front-end
and temporary \Cyclus servers on the back-end. These servers are hosted by
the Build \& Test Laboratory (BaTLab) \cite{uw_batlab_team_batlab_2014} at the University of
Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs
the following actions:

### 2015-02-18 fundamentals/intro.tex
spell check and trailing whitespaces

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
\gls{LCOE}, requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental stainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.

@@

Furthermore, modeling the evolution of a physics-dependent, international
nuclear fuel supply chain is a multiscale problem which existing tools cannot
support. They have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used-fuel
composition of fast reactor fuel. Each focus has driven the development of
specialized tools, rendering the task of answering questions between the macro
and micro levels challenging within a single tool.  In contrast, the extensible
architecture and discrete object tracking of \Cyclus allow the creation and
interchangeability of custom archetypes at any level of fidelity.

>>>>

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
\gls{LCOE}, requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental sustainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.

@@

Furthermore, modeling the evolution of a physics-dependent, international
nuclear fuel supply chain is a multi-scale problem which existing tools cannot
support. They have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used-fuel
composition of fast reactor fuel. Each focus has driven the development of
specialized tools, rendering the task of answering questions between the macro
and micro levels challenging within a single tool.  In contrast, the extensible
architecture and discrete object tracking of \Cyclus allow the creation and
interchangeability of custom archetypes at any level of fidelity.
